Refinement for open automata

### 2021-05-07 2021-Refinement/report.tex
Finished cleaning proof for lemma 1

\begin{defi}[Deadlock reduction, intuitive definition]
A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
\begin{multline*}
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
	\mpar{\everymath{\displaystyle}\begin{array}{c}
		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
	\end{array}} \\
	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
\end{multline*}
\end{defi}
This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.

@@

	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\

@@

	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V \to \values\) be such that:

@@

\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):] % TODO: proof debt, restart here
	If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
	We are left to prove \[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
	Now we additionally need to prove \goal{G2}: \(\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) before getting hypothesis \hyp{E}:
	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
	The witness of \goal{G2} is \(t_2\) obtained previously in the big disjunction, and \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) is proved by combining \hyp{p} and \hyp{g2}.
	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.

@@

% TODO

>>>>

\begin{defi}[Deadlock reduction, intuitive definition]
A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
\begin{multline*}
	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
	\mpar{\everymath{\displaystyle}\begin{array}{c}
		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
	\end{array}} \\
	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
\end{multline*}
\end{defi}
This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.

@@

	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\

@@

	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) be such that:

@@

\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):]
	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \bigcup_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:
	\begin{align*}
		\sigma \vdash R\mpar{s_1, s_2} & \text{ \hyp{1}} &
		\sigma \vdash \fguard{t_2} & \text{ \hyp{2}}
	\end{align*}
	We are left to prove:
	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'} \]
	To do that we use (\ref{eq:ID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
		\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \hyp{3}
	There are two cases in this disjunction, the second is in contradiction with \hyp{2} and the first gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{4} \]
	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.

@@

\begin{proof}[Lemma 2]
% TODO: recall what we want to prove, then prove it
\end{proof}
